% -- Introduction ------------------------------
\section{Introduction}
%
In the past few years, the term \emph{evolvable hardware (EHW)} has arised. A lot of research has been done in this new field of electronics, which utilizes \emph{evolutionary algorithms (EA)} and \emph{self-adaptive techniques}  in order to reduce or eliminate manual engineering. Reconfigurable hardware, artificial intelligence, fault tolerant and autonomous systems are brought together, enabling the system to change its architecture and behaviour dynamically and autonomously based on its internal state and its environment. By defining a specific goal or task, the system is programmed to evolve in real-time towards an implementation. Often linked with bio-inspired hardware systems, research continues in self-aware and self-adaptive systems. 

First, this paper will introduce some terminology concerning this field of research in Section \ref{sec:fundamental}. Then, it will introduce several proposed architectures for hardware implementation of evolvable systems in Section \ref{sec:discussion}. Section \ref{sec:technique} will present the techniques that are used in order to accomplish these implementations. Section \ref{sec:proposition} proposes the system design that is in our opinion the best implementation possible given the current techniques. This design will be critically analyzed in Section \ref{sec:related} using the designs presented in the discussed papers. Finally, our literature study will be wrapped up by a conclusion in Section \ref{sec:conclusion}.