%prior knowledge

\section{Prior knowledge}

[still need to give an introduction to all the matters spoken. what is evolvable hardware?]
[firstly introduce the self* properties as they are mentioned right into the discussion]

% explanation of self-aware
Self-aware adaptive computing systems are capable of adapting their behavior and resources thousands of times based on changing environmental conditions and demands \cite{selfaware}. 
This allows them to automatically accomplish their goals in the best way possible.

% what is evolvable
Evolvable systems exploiting self-adaptive techniques are self-configuring and self-optimizing systems capable of changing their operations to meet the given performance goals by modifying either the underlying heterogeneous architecture, the operating system and the self-adaptive applications. \cite{evolvable}
Meeting efficiency and accuracy constraints is getting more and more difficult , mainly because of the exponential increase of interactions among systems and the environments in which the systems are required to work. 

% what is the heartbeat 
Heartbeat makes it possible to assert performance goals as heart-rate windows each of each is delimited by a minimum and maximum heart-rate. It updates the progress of the execution calling the function that signifies a heartbeat. It monitors the progress of the execution through either a windows heart rate and a global heart-rate.\cite{evolvable}

% techniques used
The monitoring process is central to self-adaptive systems and is done by the application HeartBeats. 
Using machine learning, one can enhance synchronization techniques. K32 is a modern object-oriented operating system that responds to changing and challenging environments adapting its operations. It supports on line reconfiguration of functionalities by interposition, hot-swap and dynamic update. \cite{evolvable}

%The operating systems chooses at run-time among a set of possible implementations according %to the criteria. This decision is based on the Observe-decide-act. The need for this dynamic %choice between available implementations is give by the fact that the system is live and %lives in an unpredictable environment. \cite{selfaware}